---
output: latex_fragment
---

Here you can write the introduction of your report and include some text that will be transferred to the word file every time you re-run this Markdown

```{r}
dd <- read.csv(gzfile("../listings.csv.gz"))

dataset <- "airbnb"
```

Check the type of the R object created for the dataset

```{r}
class(dd)
```

without including the R instruction in the final document

```{r, echo=FALSE}
class(dd)
```

Get dimensions of the dataset
```{r}
dim(dd)
n<-dim(dd)[1]
K<-dim(dd)[2]

n
K
```
Check the variables

```{r}
names(dd)
```
Decide if you need to declare some more factor or date

```{r}
actives<-c(12, 15, 16, 17, 18, 22, 25, 26, 29, 33, 34, 37, 38, 40, 47, 48, 51, 52, 53, 54, 56, 57, 58, 61, 62, 63, 66, 67, 69, 74)

dd[,12]<-as.Date(dd[,12], format="%Y-%m-%d")

```


Basic descriptive analysis for numerical variables

(decide the maximum number of colors you can need in a graph based on your metadata file)
```{r, echo=FALSE}
listOfColors<-rainbow(39)

par(ask=TRUE)

for(k in actives){
  print(paste("variable ", k, ":", names(dd)[k] ))
  if (!(is.numeric(dd[,k]) || class(dd[,k])=="Date")){
    frecs<-table(as.factor(dd[,k]), useNA="ifany")
    proportions<-frecs/n
    #ojo, decidir si calcular porcentages con o sin missing values
    pie(frecs, cex=0.6, main=paste("Pie of", names(dd)[k]))
    barplot(frecs, las=3, cex.names=0.7, main=paste("Barplot of", names(dd)[k]), col=listOfColors)
    print(paste("Number of modalities: ", length(frecs)))
    print("Frequency table")
    print(frecs)
    print("Relative frequency table (proportions)")
    print(proportions)
    print("Frequency table sorted")
    print(sort(frecs, decreasing=TRUE))
    print("Relative frequency table (proportions) sorted")
    print(sort(proportions, decreasing=TRUE))
   }else{
     if(class(dd[,k])=="Date"){
       print(summary(dd[,k]))
       print(sd(dd[,k]))
       #decide breaks: weeks, months, quarters...
       hist(dd[,k],breaks="weeks")
     }else{
       hist(dd[,k], main=paste("Histogram of", names(dd)[k]))
       boxplot(dd[,k], horizontal=TRUE, main=paste("Boxplot of", names    (dd)[k]))
       print("Extended Summary Statistics")
       print(summary(dd[,k]))
       print(paste("sd: ", sd(dd[,k], na.rm=TRUE)))
       print(paste("vc: ", sd(dd[,k], na.rm=TRUE)/mean(dd[,k], na.rm=TRUE)))
      }
   }
}
par(ask=FALSE)

#per exportar figures d'R per programa
#dev.off()
#png(file=mypath,width = 950, height = 800, units = "px")
#dev.off()
```
